Cards model analysis

### 2020-04-28 cards_model_analysis.Rmd
nonhomoiconic analyses (part 1)

```{r}
parent_dir = "./presentable_results"
subdirs = c("exact_eval", "exact_eval/metaclass_lesion")
language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")

@@

```{r}
diss_figure_data = bind_rows(
  selected_lang_d %>%
    filter(run_type == "exact_eval/language") %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline"),
  selected_lang_d %>%
    filter(run_type == "exact_eval/tcnh_more_complex/language") %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline\n(task-conditioned)"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    filter(run_type == "exact_eval/metaclass_lesion") %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Meta-class lesion"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    filter(run_type == "exact_eval") %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "HoMM")) %>%
  gather(task, expected_reward, source, eval_target)
```

>>>>

```{r}
parent_dir = "./presentable_results"
subdirs = c("exact_eval", "exact_eval/metaclass_lesion", "exact_eval/nonhomoiconic")
language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")

@@

```{r}
diss_figure_data = bind_rows(
  selected_lang_d %>%
    filter(run_type == "exact_eval/language") %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline"),
  selected_lang_d %>%
    filter(run_type == "exact_eval/tcnh_more_complex/language") %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline\n(task-conditioned)"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    filter(run_type == "exact_eval/metaclass_lesion") %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Meta-class lesion"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    filter(run_type == "exact_eval/nonhomoiconic") %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Nonhomoiconic"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    filter(run_type == "exact_eval") %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "HoMM")) %>%
  gather(task, expected_reward, source, eval_target)
```
